---
title: "Final Project Data Analysis"
author: "Milan Chuttani"
date: "2024-11-16"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(sf)
library(leaflet)
library(lubridate)
library(tidyr)
library(lme4)
library(modelsummary)
library(kableExtra)
library(stargazer)

```
## === 1. SPATIAL DATA LOADING ===

```{r echo=FALSE}

# 1. Load data sets - fire perimeters and zipcodes
#       - Fire Perimeters and Buffers were compiled in QGIS. 

fire_perimeters <- st_read("./data/cleaned/CA_Megafires/CA Megafires 2020_2022_v2.shp")
zipcodes <- st_read("./data/cleaned/CA_Zipcodes_Filtered/CA_Zipcodes_Filtered.shp") %>% 
  select(-c(W_2021, A_2021,POP_SQMI, SQMI))

fire_buffers <- st_read("./data/cleaned/CA_Megafires_5mi_Buffer/CA_Megafires_5mi_Buffered.shp")

# 2. Filter for eligibility criteria 
#     - Fire is from 2020, 2021, or 2022 (Done in QGIS)
#     - Zip code pop > 500 (based on 2017 data) (Done in QGIS)
#     - Fire acres is greater than 24,000 acres or a part of a complex >24,000 acres. 
#     - the Bonny Complex and Butte Lightning Complex appear in the dataset despite being <24,000 acres. These are removed manually. 

megafires <- fire_perimeters %>% 
            filter(!(COMPLEX_NA %in% c("BONNY COMPLEX", "BUTTE LIGHTNING COMPLEX")))%>%
            select(c(OBJECTID, YEAR_, AGENCY, UNIT_ID, FIRE_NAME, ALARM_DATE, GIS_ACRES, COMPLEX_NA)) %>% 
            mutate(BURNED = 1)

buffers <- fire_buffers %>% 
            filter(!(COMPLEX_NA %in% c("BONNY COMPLEX", "BUTTE LIGHTNING COMPLEX")))%>%
            select(c(OBJECTID, YEAR_, AGENCY, UNIT_ID, FIRE_NAME, ALARM_DATE, GIS_ACRES, COMPLEX_NA)) %>% 
            mutate(BURNED = 0)
```
## === 2A. DATA CLEANING - 2020: 
```{r}
#A. Fire perimeters for 2020
megafires_2020 <- megafires %>% filter(YEAR_ == "2020")

#B1. Burned zip codes for 2020
burned_2020 <- st_intersection(zipcodes, megafires_2020)

#B2. Only keep the earliest alarm for burned 
earliest_alarm_burned_2020 <- burned_2020 %>% 
  st_drop_geometry() %>% 
  group_by(ZIP_CODE) %>% 
  summarize(EARLIEST_ALARM = min(ALARM_DATE, na.rm=TRUE))

burned_2020_filtered <- burned_2020 %>%
  inner_join(earliest_alarm_burned_2020, by = c("ZIP_CODE" = "ZIP_CODE", "ALARM_DATE" = "EARLIEST_ALARM"))

#C1. Adjacent zip codes for 2020
buffered_2020 <- buffers %>% filter(YEAR_=="2020")
adjacent_2020 <- st_intersection(zipcodes, buffered_2020) %>% 
        filter(!(ZIP_CODE %in% burned_2020$ZIP_CODE))

#C2. Keep only the earliest alarm for adjacent
earliest_alarm_adjacent_2020 <- adjacent_2020 %>% 
  st_drop_geometry() %>% 
  group_by(ZIP_CODE) %>% 
  summarize(EARLIEST_ALARM = min(ALARM_DATE, na.rm=TRUE))

adjacent_2020_filtered <- adjacent_2020 %>%
  inner_join(earliest_alarm_adjacent_2020, by = c("ZIP_CODE" = "ZIP_CODE", "ALARM_DATE" = "EARLIEST_ALARM"))

# E. Final data cleaning - If two fires in the same zip code start at the same date, then remove the smaller fire manually
#   - 2 zipcodes from burned_2020_filtered; 0 zipcodes from adjacent zipcodes. 

burned_2020_filtered <- burned_2020_filtered %>% 
  filter(!OBJECTID %in% c(1214, 1196))

# F. Create a "combined" dataset and add to a single dataset

combined <- rbind(burned_2020_filtered, adjacent_2020_filtered)
```

## === 2B. Data Cleaning - Repeat for 2021: 
```{r}
#A. Fire perimeters for 2021
megafires_2021 <- megafires %>% filter(YEAR_ == "2021")

#B1. Burned zip codes for 2020
burned_2021 <- st_intersection(zipcodes, megafires_2021)

#B2. Only keep the earliest alarm for burned 
earliest_alarm_burned_2021 <- burned_2021 %>% 
  st_drop_geometry() %>% 
  group_by(ZIP_CODE) %>% 
  summarize(EARLIEST_ALARM = min(ALARM_DATE, na.rm=TRUE))

burned_2021_filtered <- burned_2021 %>%
  inner_join(earliest_alarm_burned_2021, by = c("ZIP_CODE" = "ZIP_CODE", "ALARM_DATE" = "EARLIEST_ALARM"))

#C1. Adjacent zip codes for 2020
buffered_2021 <- buffers %>% filter(YEAR_=="2021")
adjacent_2021 <- st_intersection(zipcodes, buffered_2021) %>% 
        filter(!(ZIP_CODE %in% burned_2021$ZIP_CODE))

#C2. Keep only the earliest alarm for adjacent
earliest_alarm_adjacent_2021 <- adjacent_2021 %>% 
  st_drop_geometry() %>% 
  group_by(ZIP_CODE) %>% 
  summarize(EARLIEST_ALARM = min(ALARM_DATE, na.rm=TRUE))

adjacent_2021_filtered <- adjacent_2021 %>%
  inner_join(earliest_alarm_adjacent_2021, by = c("ZIP_CODE" = "ZIP_CODE", "ALARM_DATE" = "EARLIEST_ALARM"))

# E. Final data cleaning - No need for 2021

# F. Merge with the "combined" dataset

combined <- rbind(combined, burned_2021_filtered)
combined <- rbind(combined, adjacent_2021_filtered)

```

## === 2C. Data Cleaning - Repeat for 2022: 
```{r}
#A. Fire perimeters for 2022
megafires_2022 <- megafires %>% filter(YEAR_ == "2022")

#B1. Burned zip codes for 2022
burned_2022 <- st_intersection(zipcodes, megafires_2022)

#B2. Only keep the earliest alarm for burned 
earliest_alarm_burned_2022 <- burned_2022 %>% 
  st_drop_geometry() %>% 
  group_by(ZIP_CODE) %>% 
  summarize(EARLIEST_ALARM = min(ALARM_DATE, na.rm=TRUE))

burned_2022_filtered <- burned_2022 %>%
  inner_join(earliest_alarm_burned_2022, by = c("ZIP_CODE" = "ZIP_CODE", "ALARM_DATE" = "EARLIEST_ALARM"))

#C1. Adjacent zip codes for 2022
buffered_2022 <- buffers %>% filter(YEAR_=="2022")
adjacent_2022 <- st_intersection(zipcodes, buffered_2022) %>% 
        filter(!(ZIP_CODE %in% burned_2022$ZIP_CODE))

#C2. Keep only the earliest alarm for adjacent
earliest_alarm_adjacent_2022 <- adjacent_2022 %>% 
  st_drop_geometry() %>% 
  group_by(ZIP_CODE) %>% 
  summarize(EARLIEST_ALARM = min(ALARM_DATE, na.rm=TRUE))

adjacent_2022_filtered <- adjacent_2022 %>%
  inner_join(earliest_alarm_adjacent_2022, by = c("ZIP_CODE" = "ZIP_CODE", "ALARM_DATE" = "EARLIEST_ALARM"))

# E. Final data cleaning - If two fires in the same zip code start at the same date, then remove the smaller fire.
#   - 2 zipcodes from burned_2022_filtered 
#   - 1 zipcodes from adjacent_2022_filtered

burned_2022_filtered <- burned_2022_filtered %>% 
  filter(!OBJECTID == 495)

adjacent_2022_filtered <- adjacent_2022_filtered %>% 
  filter(!(OBJECTID == 495 & ZIP_CODE == 95527))

# F. Merge with the "combined" dataset

combined <- rbind(combined, burned_2022_filtered)
combined <- rbind(combined, adjacent_2022_filtered)
```

## === 2D Data Cleaning - Calculating Months: 
```{r echo=FALSE}
start_date <- as.Date("2019-07-01")

# If an alarm date is after the 25th of a month, then set "Month 0" as the next month. Otherwise, keep Month 0 as the month of the alarm date. 
combined <- combined %>% mutate(SIMPLIFIED_ALARM_DATE  = if_else(
        day(ALARM_DATE) >= 25,
        # Set to the first day of the next month if after the 25th
        floor_date(ALARM_DATE + months(1), "month"),
        # Otherwise, set to the first day of the current month
        floor_date(ALARM_DATE, "month")
      ))

combined <- combined %>% mutate(MONTH_AFTER_START =  floor(time_length(interval(start_date, SIMPLIFIED_ALARM_DATE), "months"))) 

combined_zip <- combined %>% st_drop_geometry()

```

## === 2. DATA CLEANING - MERGE WITH NET MIGRATION DATA ===
```{r}
# Helper Function: Searches the migration table for the 6 months before and after each wildfire - aggregates in the main zip table.  

aggregate_migration_month <- function(ref_month, zipcode, migrations) {
  # Define the 6-month windows
  start_before = ref_month - 6
  start_after = ref_month
  end_after = ref_month + 6

  # Calculate net migration for the periods. Month 0 (the reference month) is included in "After".
  total_before <- migrations %>%
    filter(MONTH_AFTER_START >= start_before & MONTH_AFTER_START < start_after & ZIPCODE == !!zipcode) %>%
    summarise(total_before = sum(NET.MIGRATION, na.rm = TRUE)) %>%
    pull(total_before)

  total_after <- migrations %>%
    filter(MONTH_AFTER_START >= start_after & MONTH_AFTER_START < end_after & ZIPCODE == !!zipcode) %>%
    summarise(total_after = sum(NET.MIGRATION, na.rm = TRUE)) %>%
    pull(total_after)

  list(total_before = total_before, total_after = total_after)
}

# 4. Load in migration data 

Y2019 <- read.csv("./data/Change of Address Data/Y2019.csv") %>% 
    filter(ZIPCODE %in% combined$ZIP_CODE) %>% 
    select(c(YYYYMM, ZIPCODE, CITY, TOTAL.FROM.ZIP, TOTAL.TO.ZIP))
Y2020 <- read.csv("./data/Change of Address Data/Y2020.csv") %>% 
    filter(ZIPCODE %in% combined$ZIP_CODE) %>% 
    select(c(YYYYMM, ZIPCODE, CITY, TOTAL.FROM.ZIP, TOTAL.TO.ZIP))
Y2021 <- read.csv("./data/Change of Address Data/Y2021.csv") %>% 
    filter(ZIPCODE %in% combined$ZIP_CODE) %>% 
    select(c(YYYYMM, ZIPCODE, CITY, TOTAL.FROM.ZIP, TOTAL.TO.ZIP))
Y2022 <- read.csv("./data/Change of Address Data/Y2022.csv") %>% 
    filter(ZIPCODE %in% combined$ZIP_CODE) %>% 
    select(c(YYYYMM, ZIPCODE, CITY, TOTAL.FROM.ZIP, TOTAL.TO.ZIP))
Y2023 <- read.csv("./data/Change of Address Data/Y2023.csv") %>% 
    filter(ZIPCODE %in% combined$ZIP_CODE) %>% 
    select(c(YYYYMM, ZIPCODE, CITY, TOTAL.FROM.ZIP, TOTAL.TO.ZIP))


tmp_migration <-  do.call("rbind", list(Y2019, Y2020, Y2021, Y2022, Y2023))
combined_migration <- tmp_migration %>% mutate(NET.MIGRATION = TOTAL.TO.ZIP - TOTAL.FROM.ZIP)


# Begin rearranging data to combine migration and zipcode data
combined_migration <- combined_migration %>% mutate(
    # Convert the number format YYYYMM to a Date object representing the first of that month
    DATE = ym(as.character(YYYYMM)))

combined_migration <- combined_migration %>% mutate(MONTH_AFTER_START =  floor(time_length(interval(start_date, DATE), "months")))

# Aggregate 8 month before and after calculations.
data_1 <- combined_zip %>%
  rowwise() %>%
  mutate(
    totals = list(aggregate_migration_month(MONTH_AFTER_START, ZIP_CODE, combined_migration))
  ) %>%
  mutate(
    total_before = totals$total_before,
    total_after = totals$total_after
  ) %>%
  select(-totals)


# Calculate percentages of total population

data_1 <- data_1 %>% mutate(percent_before = (total_before*100)/POPULATION, 
                            percent_after = (total_after*100)/POPULATION)


```

## === Draw Descriptive Plots
### 1. Scatter plot showing over the months average change in percentages
```{r}

# Join tables on zipcodes
combined_migration$ZIPCODE <- as.character(combined_migration$ZIPCODE)

scatter <- combined_zip %>%
  inner_join(combined_migration, by = c("ZIP_CODE" = "ZIPCODE"))

scatter <- scatter %>% rename(MONTH_FIRE = MONTH_AFTER_START.x, 
                              MONTH_MIGRATION = MONTH_AFTER_START.y)


# Calculate the relative months: difference between months
scatter <- scatter %>%
  mutate(
    months_difference = MONTH_MIGRATION - MONTH_FIRE,
    within_window = months_difference >= -8 & months_difference <= 7,
    percent_migration = (100*NET.MIGRATION)/POPULATION
  ) %>%
  filter(within_window)

#Make plot - zoomed in
plot_zoomed <- ggplot(scatter, aes(x = months_difference, y = percent_migration, color = factor(BURNED))) +
  geom_point(position = position_jitter(width = 0.15, height = 0), alpha=0.3) +
  scale_color_manual(values = c("blue", "red")) +
  geom_smooth(method = "loess", span = 0.25, se = TRUE) +  # LOESS curve
  geom_vline(xintercept = 0, linetype = "dashed", color = "yellow") +
  coord_cartesian(ylim = c(-4, 4)) +
  theme_minimal() +  
  labs(title = "Net Migration by Month: Control and Treatment Groups, 2020 - 2022",
       x = "Months Relative to the Start of a Megafire",
       y = "Net Migration as Percent of Total Population (%)",
       color = "Burned")

plot_zoomed

#Make plot - full
plot_full <- ggplot(scatter, aes(x = months_difference, y = percent_migration, color = factor(BURNED))) +
  geom_point(position = position_jitter(width = 0.3, height = 0), alpha=0.5) +
  scale_color_manual(values = c("blue", "red")) +
  geom_smooth(method = "loess", span = 0.25, se = TRUE) +  # LOESS curve
  theme_minimal() +  
  labs(title = "Net Migration by Month: Control and Treatment Groups, 2020 - 2022",
       x = "Months Relative to the Start of a Megafire",
       y = "Net Migration as Percent of Total Population (%)",
       color = "Burned")
plot_full
```

### 2. Box Plot and Difference-In-Difference Plots

```{r}

# Reshape the data to long format
data_1_long <- data_1 %>%
  pivot_longer(cols = c(percent_before, percent_after), 
               names_to = "time", 
               values_to = "percent_change")

data_1_long <- data_1_long %>% mutate(time = ifelse(time == "percent_before", 0, 1))

data_1_long <- data_1_long %>%
  mutate(group_time = factor(paste(ifelse(BURNED == 0, "Control", "Treatment"), 
                                   "Time", time, sep = "-"),
                             levels = c("Control-Time-0", "Control-Time-1",
                                        "Treatment-Time-0", "Treatment-Time-1")))

medians <- data_1_long %>%
  mutate(group_time = factor(paste(ifelse(BURNED == 0, "Control", "Treatment"), 
                                   "Time", time, sep = "-"),
                             levels = c("Control-Time-0", "Control-Time-1",
                                        "Treatment-Time-0", "Treatment-Time-1"))) %>%
  group_by(group_time, BURNED) %>%
  summarise(median_percent_change = median(percent_change, na.rm = TRUE))

#Fix Labels
new_labels <- c(
  "Control-Time-0" = "Control: Megafire Adjacent (Before)",
  "Control-Time-1" = "Control: Megafire Adjacent (After)",
  "Treatment-Time-0" = "Treatment: Megafire Affected (Before)",
  "Treatment-Time-1" = "Treatment: Megafire Affected (After)"
)

# Plot with adjusted x-axis
ggplot(data_1_long, aes(x = group_time, y = percent_change, fill = factor(BURNED))) +
  geom_boxplot(outlier.shape = NA) +
  geom_line(data = medians, aes(x = group_time, y = median_percent_change, 
                                group = BURNED, color = factor(BURNED)), 
            position = position_dodge(width = 0.75)) +
    coord_cartesian(ylim = c(-4, 4)) +
  scale_fill_manual(values = c("blue", "red")) +  # Set fill colors for Burned groups
  scale_color_manual(values = c("blue", "red")) +  # Set line colors matching fill
  scale_x_discrete(labels = new_labels) +  # Custom x-axis labels
  labs(
    title = "Distribution of Percent Change Before and After",
    x = "Group and Time",
    y = "Percent Change",
    fill = "Burned"
  ) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels


# ========Difference in Difference 


# Assuming `data_1_long` is preprocessed correctly
# Calculate means and SE for period and burned groups
means_se <- data_1_long %>%
  group_by(group_time, BURNED) %>%
  summarise(
    mean_change = mean(percent_change, na.rm = TRUE),
    se = sd(percent_change, na.rm = TRUE) / sqrt(n())
  )

# Adding separate time and group variables
means_se <- means_se %>% 
  mutate(
    Time = ifelse(grepl("0", group_time), "Before", "After"),
    Group = ifelse(grepl("Control", group_time), "Control (adjacent to megafire)", "Treatment (burned by megafire)")
  )

means_se$Time <- factor(means_se$Time, levels = c("Before", "After"))


# Create the plot with x for Time and separate dodging for Groups
did_plot <- ggplot(means_se, aes(x = Time, y = mean_change, color = Group, group = Group)) +
  geom_point(size = 3, position = position_dodge(width = 0)) +  # Points for means
  geom_errorbar(aes(ymin = mean_change - se, ymax = mean_change + se),
                width = 0.2, position = position_dodge(width = 0)) +  # Error bars
  geom_line(position = position_dodge(width = 0)) +  # Lines connecting means
  scale_color_manual(values = c("blue", "red")) +  # Set line and point colors
  labs(
    title = "Difference-in-differences: Causal effect of megafire damage on net migration",
    x = "Time (6-month period relative to megafire)",
    y = "Net Migration as Percent of Total Population (%)",
    color = "Group"
  ) +
  theme_minimal()


did_plot
```

### 3. Summary Table for Results 

```{r}
# Calculate SD, Mean, Etc. for each grouping

standard_error <- function(x) {
  sd(x) / sqrt(length(x))
}

summary_table <- data_1_long %>%
  group_by(time, BURNED) %>%
  summarise(
    mean = round(mean(percent_change, na.rm = TRUE), 3),
    sd = round(sd(percent_change, na.rm = TRUE), 3),
    se = round(standard_error(percent_change), 3),
    n = n()
  )

summary_table <- summary_table %>%
  rename(
    `Time Period` = time,
    `Burned by Wildfire?` = BURNED,
    `Number of Zip Codes` = n,
    Mean = mean,
    SD = sd,
    SE = se
  ) %>%
  mutate(`Time Period` = ifelse(`Time Period` == 0, "Before", "After"),
         `Burned by Wildfire?` = ifelse(`Burned by Wildfire?` == 0, "No", "Yes")) %>%
  arrange(desc(`Burned by Wildfire?`))
  

# Format table for publication
formatted_table <- summary_table %>%
  kable("html", caption = "Summary Statistics of Percent Change in Net Migration by Time Period and Burn Status") %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(3:6, background = "lightgrey") %>%  # Background color for columns
  footnote(general = "Wildfire-affected zipcodes, our treatment group, were burned by a megafire. Wildfire-adjacent zipcodes, our control group, were not burned by a megafire but fell within 5 miles of the fire perimeter. Our time calculations aggregate net-migration across  6 months before and during/after a megafire.",general_title = "Table Note: ")
# Print the table
formatted_table

```
# === Results: Running the Models:

### Part 1: Diff in Diff
```{r}

# Part 1: Diff in Diff

mod1 <- lm(percent_change ~ BURNED, data=data_1_long)
mod2 <- lm(percent_change ~ time, data=data_1_long)


mod3 <- lm(percent_change ~ BURNED * time, data = data_1_long)
summary(mod3)
modelsummary(list(mod1, mod2, mod3), stars = TRUE)

stargazer(mod1, mod2, mod3, type = "text",
          column.labels = c("Treatment Only", "Time Only", "Diff-in-Diff"),
          model.numbers = TRUE,
          dep.var.labels = "Net Migration (%)",
          covariate.labels = c("Burned by Megafire", "Post Fire Time Period", "Burned by Megafire x Post Fire"),
          keep.stat = c("n"),
          title="Table 2: Difference in Differences: Model of Causal Effect of Megafire Damage on Zipcode Net-Migration ",
          out="part1-diff-in-diff.html")

```

### Part 2: Multilevel Mixed Effects Models

```{r}

histogram_acres <- ggplot(megafires, aes(x=GIS_ACRES)) + 
  geom_histogram(bins=15, fill="lightgreen", color="black") + 
  ylab("Frequency") + xlab("Acres Burned") + ggtitle("Number of acres burned per CA megafire: 2020 - 2022 (n=45)")
histogram_acres

histogram_population <- ggplot(data_1, aes(x=POPULATION)) + 
  geom_histogram(bins=15, fill="lightgreen", color="black") + 
  ylab("Frequency") + xlab("Population of Zipcode") + ggtitle("Population of Included Zipcodes (n=272)")
histogram_population

```

```{r}
df <- data_1_long %>% filter(time == 1)
df <- df %>% mutate(FIRE_NAME = as.factor(FIRE_NAME))

mod1 <- lmer(percent_change ~ log(POPULATION) + (1|FIRE_NAME), data = df, REML = FALSE)
summary(mod1)

mod2 <- lmer(percent_change ~ log(POPULATION) + BURNED + (1|FIRE_NAME), data = df, REML = FALSE)
summary(mod2)

mod3 <- lmer(percent_change ~ log(POPULATION) + BURNED + log(GIS_ACRES) + (1|FIRE_NAME), data = df, REML = FALSE)
summary(mod3)

#same with sigam2_u and sigma2_e
temp <- do.call(rbind, lapply(list(mod1, mod2, mod3), FUN = function(x) data.frame(VarCorr(x))))
sigma2_u <- round(temp$vcov[c(1, 3, 5)], 3)
#sigma2_u <- c("", sigma2_u)
#sigma2_u <- sigma2_u[c(2, 1, 3, 4)]

sigma2_e <- round(temp$vcov[c(2, 4, 6)], 3)
#sigma2_e <- c("", sigma2_e)
#sigma2_e <- sigma2_e[c(2, 1, 3, 4)]

#Generate model building tables
stargazer(mod1, mod2, mod3, type = "text",
          column.labels = paste("Model", 1:3),
          model.numbers = FALSE,
          keep = c("Constant", "POPULATION", "BURNED", "GIS_ACRES"),
          keep.stat = c("n"),
          title="Table 3: Multilevel Mixed-Effects Models of Post-Megafire Net Migration",
          out="part2-random-effects-output.html",
          add.lines = list(c("sigma2u", sigma2_u),
                           c("sigma2e", sigma2_e)))

# Calculate ICC for mod3

# Extract variance components
variance_components <- VarCorr(mod3)

VarCorr(mod1)
VarCorr(mod2)
VarCorr(mod3)

# Extract the variances
fire_variance <- as.numeric(variance_components$FIRE_NAME[1])
residual_variance <- attr(variance_components, "sc")^2

ICC <- fire_variance / (fire_variance + residual_variance)

```

## == Double check filtering in Leaflet ==
```{r}

reset_crs <- function(data){
  crs_target <- 4326

  if (st_crs(data)$epsg != crs_target) {
    tmp <- st_transform(data, crs_target)
  }
  return(tmp)
}

adjacent <- reset_crs(adjacent_2020)
burned <- reset_crs(intersected_2020)
perimeters <- reset_crs(megafires)

combined_map <- reset_crs(combined)

burned_combined <- combined_map %>% filter(BURNED==1)
adjacent_combined <- combined_map %>% filter(BURNED==0)


# Transform to WGS 84 (EPSG:4326) if necessary
# if (st_crs(adjacent_2020)$epsg != crs_target) {
#   adjacent_2020 <- st_transform(adjacent_2020, crs_target)
# }
# 
# if (st_crs(buffered_2020)$epsg != crs_target) {
#   fire_perimeters <- st_transform(fire_perimeters, crs_target)
# }
# 
# if (st_crs(fire_perimeters)$epsg != crs_target) {
#   fire_perimeters <- st_transform(fire_perimeters, crs_target)
# }

map <- leaflet() %>%
    addProviderTiles(providers$CartoDB.Positron) %>%
    addPolygons(data = adjacent_combined, 
                color = "blue", 
                weight = 1, 
                opacity = 0.5, 
                fillOpacity = 0.2, 
                group = "Zipcodes")%>%
   addPolygons(data = burned_combined, 
                color = "red", 
                weight = 1, 
                opacity = 0.5, 
                fillOpacity = 0.2, 
                group = "Zipcodes")%>%
    addPolygons(data = perimeters, 
                color = "black", 
                weight = 1, 
                opacity = 0.5, 
                fillOpacity = 0.2, 
                group = "Fire Perimeters") %>%
  addLayersControl(
    overlayGroups = c("Zipcodes", "Fire Perimeters"),
    options = layersControlOptions(collapsed = FALSE)
  )

map

```

## Appendix - Exploratory Case Studies from Select Zipcodes

```{r cars}
Y2019 <- read.csv("./data/Change of Address Data/Y2019.csv") %>% 
    filter(ZIPCODE %in% primary_zipcodes) %>% 
    select(c(YYYYMM, ZIPCODE, CITY, TOTAL.FROM.ZIP, TOTAL.TO.ZIP))
Y2020 <- read.csv("./data/Change of Address Data/Y2020.csv") %>% filter(ZIPCODE %in% primary_zipcodes) %>% 
    select(c(YYYYMM, ZIPCODE, CITY, TOTAL.FROM.ZIP, TOTAL.TO.ZIP))
Y2021 <- read.csv("./data/Change of Address Data/Y2021.csv") %>% 
    filter(ZIPCODE %in% primary_zipcodes) %>% 
    select(c(YYYYMM, ZIPCODE, CITY, TOTAL.FROM.ZIP, TOTAL.TO.ZIP))
Y2022 <- read.csv("./data/Change of Address Data/Y2022.csv") %>% 
    filter(ZIPCODE %in% primary_zipcodes) %>% 
    select(c(YYYYMM, ZIPCODE, CITY, TOTAL.FROM.ZIP, TOTAL.TO.ZIP))

combined_all <-  do.call("rbind", list(Y2019, Y2020, Y2021, Y2022))

combined_all <- combined_all %>% mutate(NET.MIGRATION = TOTAL.TO.ZIP - TOTAL.FROM.ZIP)

#North Complex Fire - 

graphFire <- function(zipcode, month, firename){
  location <- combined_all %>% filter(ZIPCODE == zipcode)
  location$MONTH <- 1:nrow(location)
  print(location)

  
  ggplot(location, aes(x = MONTH, y = NET.MIGRATION)) +
    geom_bar(stat = "identity", fill = "skyblue", color = "black") +
    theme_minimal() +
    labs(title = paste0("Net Migration by Month: ", firename, " - ", zipcode),
         x = "Month",
         y = "Net Migration") + 
    geom_vline(xintercept = month, linetype = "dashed", color = "red")   # Add a vertical dashed line
}


graphFire(95636, 21, "Caldor Fire")
graphFire(95684, 21, "Caldor Fire")
graphFire(95916, 13, "North Complex Fire")
graphFire(95947, 24, "Dixie Fire")
#graphFire(94576, 1, "Glass Fire") Deer Park no data
graphFire(94574, 15, "Glass Fire")
graphFire(94558, 14, "LNU Lightning Complex Fire")

```
